Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Updated Figure 13 layout b

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  )  +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.2,
  axis_pos_x = -0.55,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, -0.3)) +
  ylim(c(0, -0.38)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

five_gau_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.75, -0.35)) +
  ylim(c(-0.75, -0.4)) +
  interior_annotation("b3", 
                      position = c(0.08, 0.9),
                      cex = 2)

>>>>

trimesh_removed_gau_umap <- ggplot() + 
  geom_segment(data = tr_from_to_df_gau1, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c",
               linewidth = 1) +
  geom_point(
    data = umap_gau_scaled,
    aes(
      x = UMAP1,
      y = UMAP2
    ),
    alpha = 0.05,
    #size = 0.1,
    color = "#000000"
  )  +
  interior_annotation("b1", 
                      position = c(0.06, 0.95),
                      cex = 2) +
  theme(
    aspect.ratio = 1
  )

@@

axes_obj <- gen_axes(  
  proj = projection,
  limits = 0.3,
  axis_pos_x = -0.58,
  axis_pos_y = -0.05,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.64, -0.26)) +
  ylim(c(0, -0.38)) +
  interior_annotation("b2", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

five_gau_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.75, -0.4)) +
  ylim(c(-0.75, -0.4)) +
  interior_annotation("b3", 
                      position = c(0.08, 0.9),
                      cex = 2)
